---
title: "Tutorial: Machine Learning Recap"
author: Linda T. Betz, M.Sc.
date: June 29, 2021
output: 
  beamer_presentation:
    theme: "Boadilla"
    colortheme: "seahorse"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})


library(tidyverse)
library(mlr)

```

# Structure of the tutorial
- x (today): introduction to basic R syntax and priniciples, data cleaning and wrangling
- x: Machine Learning in R (part I)
- x: Machine Learning in R (part II), working on your reports

# Today's tutorial ...
... is based on the mlr3 book (https://mlr3book.mlr-org.com/index.html).

# Machine Learning in a nutshell
add

# Tasks
Tasks encapsulate the data set and other relevant information about a machine learning problem, for example the name of the target variable for supervised problems.

Different types of tasks (depending on the problem): classification tasks, regression tasks, survival analysis tasks, cluster analysis tasks...


# Tasks
Example: binary classification task for breast cancer (benign vs. malignant)
```{r, include=TRUE, size="tiny"}
data(BreastCancer, package = "mlbench") # load data
classif.task <- makeClassifTask(id = "BreastCancer", data = BreastCancer %>% select(-Id), target = "Class")
classif.task
```

# Learner
 A learner is a machine learning algorithm. Most of the popular learners can generally be used for both classification and regression (e.g. SVM, Random Forests, kNN, ...).
```{r, include=TRUE, size="tiny"}
# classification random forest, set it up for predicting probabilities
classif.lrn <- makeLearner("classif.randomForest", predict.type = "prob")
classif.lrn
```
